sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-12-09 doc/paper.Rmd
Add ref

Spatially and spatiotemporally explicit data are increasingly collected in ecology and have the power to reveal new ecological processes [e.g., @english2021] (OTHER REF?) and improve ecological management [@sofaer2019].
These data present statistical challenges to modelling them effectively and efficiently; appropriate models such as GLMMs with random fields are often computationally intensive and challenging to implement, interpret, and evaluate.
We hope the development of user-friendly interfaces such as sdmTMB opens this useful class of models to a wider audience of users.

>>>>

Spatially and spatiotemporally explicit data are increasingly collected in ecology and have the power to reveal new ecological processes [e.g., @dinnage2020; @english2021] and improve ecological management [@sofaer2019].
These data present statistical challenges to modelling them effectively and efficiently; appropriate models such as GLMMs with random fields are often computationally intensive and challenging to implement, interpret, and evaluate.
We hope the development of user-friendly interfaces such as sdmTMB opens this useful class of models to a wider audience of users.
